First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-05-14 ms.tex
Major additions to text to explain slice figure, also minor tweaks

\begin{abstract}
The Murchison Widefield Array (MWA) has collected hundreds of hours of Epoch of 
Reionization (EoR) data and now faces the challenge of overcoming foreground and 
systematic contamination to reduce the data to a cosmological measurement. We introduce 
several novel analysis techniques such as cable reflection calibration, high resolution 
gridding kernels, diffuse foreground model subtraction, and quality control methods. Each 
change to the analysis pipeline is tested against a two dimensional power spectrum figure 
of merit to demonstrate improvement. We incorporate the new techniques into a deep 
integration of 32 hours of MWA data. This data set is used to place a systematic-limited 
upper limit on the cosmological power spectrum of $\Delta^2 \leq 2.17 \times 10^4$ mK
$^2$ at $k=0.24$ h~Mpc$^{-1}$ and $z=6.8$, consistent with other published limits, and a 
modest improvement (factor of 1.7) over previous MWA results. While our result is 
systematic limited, we identify several strategies to overcome these systematics in future 
analysis.
\end{abstract}
\keywords{cosmology: observations - cosmology: reionization}
\maketitle

@@

\section{Analysis Pipeline}\label{sec:analysis}
In order to ensure consistency in analysis, the international MWA EoR collaboration has 
defined two independent reference analysis pipelines. The details of this strategy are 
outlined in D.~C.~Jacobs et al. 2016 (in review). This study is based on the FHD-to-
\eppsilon pipe, which is in turn based on the Fast Holographic Deconvolution (FHD
\footnote{\url{https://github.com/miguelfmorales/FHD}}, \citealt{Sullivan:2012}) and Error 
Propagated Power Spectrum with Interleaved Observed Noise (\eppsilon
\footnote{\url{https://github.com/miguelfmorales/eppsilon}}, B.~J.~Hazelton et al. 2016, in 
prep) packages. The general flow of the pipeline is shown in Figure~\ref{fig:pipe}, and we 
give an overview below.

@@

Under these assumptions we can express the measured, uncalibrated visibility for an 
antenna pair $(i,j)$ as
\begin{equation}
V'_{ij}(\nu) \approx g_i(\nu)g^*_jV_{ij}(\nu),
\end{equation}
where $g_i(\nu)$ and $g_j(\nu)$ are the complex gains for antennas $i$ and $j$ 
respectively. Because we are treating polarizations independently, we allow the antenna 
subscript to run over both East-West (E-W) and North-South (N-S) polarizations.

@@

The gridded $uv$ data are then Fourier transformed to create sky-frame images. To avoid 
aliasing we image out 90$^\circ$ from phase center (gridding resolution of a half 
wavelength), and crop the image. We found that cropping the image based on beam value 
resulting in hard edges in integrated images from different snapshots having beams pointed 
in slightly different directions. To avoid the hard edges, we predetermine a set of HEALPix 
pixels to interpolate to, and use the same set for all snapshots on a given field. The final 
cropped field of view for this work is a 21$^\circ$ square centered at RA~$=0$ h, dec~
$=-27^\circ$.

@@

\begin{figure}
\begin{center}
\subfigure{\includegraphics[width=.9\columnwidth]{fourth_line_pre.pdf}}
~
\subfigure{\includegraphics[width=.9\columnwidth]{fourth_line_post.pdf}}
\caption{
\emph{Top:} Single polarization dirty power spectrum formed from the golden data set, 
before implementing cable reflection fitting into the calibration loop. The black arrow points 
to a horizontal band at $k_{||} \approx 0.6$~h~Mpc$^{-1}$, which cannot be accounted for 
by the coarse bands. \emph{Bottom:} After we implement the cable reflection fitting in our 
calibration solutions, we see the reflection line disappears.
\label{fig:cables}
}
\end{center}
\end{figure}

@@

\subsection{Gridding Kernel Resolution}
A similar, low level effect which had the potential to contaminate the EoR window is shown 
in Figure~\ref{fig:beam_res}. The spectra shown are the \emph{model} spectra -- calculated 
by propagating the sky model visibilities through the entire pipeline. Despite our foreground 
model not containing spectral structure, the EoR window in the left panel seems to have a 
floor at a level $\sim 10^7$~mK$^2$~h$^{-3}$~Mpc$^3$, comparable to predicted EoR 
signals. In addition there is a faint line in the upper-left of the plot which has the same slope 
as the wedge, but seems to originate far beyond the horizon.

@@

The source of this floor and super-horizon line ended up being the resolution at which we 
formed the gridding kernel when gridding visibilities. In the interest of computational speed 
and efficiency, the kernel is pre-calculated at a high resolution, then a nearest neighbor 
lookup table is used to approximate the beam values at discrete pixels. The kernel 
resolution used in the top panel of Figure~\ref{fig:beam_res} was 0.04 wavelengths -- much 
smaller than the half wavelength grid corresponding to horizon to horizon imaging. 
However, as a baseline migrates in $\emph{uv}$ coordinates across frequencies, it 
undergoes discrete steps between kernel values used. This effectively results in small 
baseline position errors which shift periodically in frequency, resulting in power being thrown 
up into the window and a relatively strong harmonic at the frequency of the shifting (the faint 
line in the upper left of the window). While we illustrate this effect with a model power 
spectrum, the same problem exists in the data, but is below the noise levels at three hours 
of integration.

@@

It has been shown that subtracting a foreground model strictly within the main lobe of the 
primary beam will not be sufficient to suppress the power spectrum wedge and unlock the 
EoR window \citep{Pober:2016, Thyagarajan:2015, Thyagarajan:2015b}. In principle we 
can repeat the model building described above using additional MWA observations pointed 
away from our field of interest. But until that work is complete we supplement the extent of 
our point source model using additional catalogs. We accomplish this through a hierarchical 
catalog pulling from our early KGS catalog, the MWA Commissioning Survey\footnote{The 
more complete GLEAM Survey \citep[][Hurley-Walker et al., in collaboration review]
{Wayth:2015} was not available at the time of analysis.} \citep[MWACS, ][]
{Hurley-Walker:2014}, Culgoora \citep{Slee:1977}, and the Molonglo Reference Catalog 
\citep[MRC, ][]{Large:1981}. Source fluxes are prioritized in this order based on our 
confidence in their predicted flux at 182 MHz. We first cluster the source lists to avoid 
redundant sources, using a 3.5 arcmin neighborhood radius, then select the flux from the 
highest priority catalog. Spectral indices were obtained from the MWACS and Culgoora 
catalogs when available, otherwise a two-point spectral index was estimated for Culgoora-
MRC matches or MRC-SUMSS matches. All other sources were given a spectral index of 
$-0.8$. The spectral index was used to extrapolate the flux from the catalog frequency to 
182 MHz, but a uniform spectral index of $-0.8$ is used within our band when forming 
model visibilities for calibration and foreground subtraction.

@@

Because we use the input foreground model to calibrate our visibilities, the gain estimates 
for our two runs differed. In particular we saw the overall flux scale of the calibrated 
visibilities was higher when using the full hierarchical catalog. In order to put both residual 
2D power spectra onto the same scale for comparison, we first divide each pixel by the 
corresponding dirty power spectrum pixel, then subtract to arrive at a ratio difference. 
\begin{equation}\label{eq:diff_ratio}
\mathtt{ratio\;difference = \frac{residual_1}{dirty_1} - \frac{residual_2}{dirty_2}}
\end{equation}
Here we use subscript 1 to represent the MWACS catalog spectra, and 2 for the 
hierarchical catalog spectra. The ratio difference is shown in Figure~\ref{fig:mwacs_ratio}. 
The entire wedge being positive (blue) demonstrates that using the new catalog resulted in 
successfully subtracting higher fractional power. Not only does this indicate we subtract 
more power, but it also confirms that our calibrated data is more closely matched to the 
model, meaning that the higher flux scale seen in the left panel of Figure~
\ref{fig:mwacs_diff}, and our calibration solutions in general, are more accurate.

@@

We use the jackknife method -- dividing the data into many subgroups -- to filter out bad 
data and detect patterns. A powerful grouping is to divide the data into the observation day 
and ``pointing" (which direction the antennas were pointed while tracking the EoR0 field). 
We show an example of one day's worth of per-pointing power spectra in Figure~
\ref{fig:jackknife}. The pointings are labeled sequentially with $-5$ corresponding to five 
pointing steps prior to zenith transit, $0$ corresponding to zenith, and $+4$ corresponding 
to four steps after zenith. Early in the night ($-5$ through $-3$) the bulk of the galactic plane 
was still above the horizon, and despite being very far from our primary field of view, highly 
contaminated our observations through the sidelobes of the instrument. We then have 
relatively well behaved pointings, with the EoR window dominated by noise, until the final 
pointing of the night when we can see evidence of the galaxy rising again indicated by 
strong lines of power at the edge of the foreground wedge. We saw the same contamination 
on all days of observation and decided to cut all $-5$, $-4$, $-3$, and $+4$ pointings from 
our data set. In principle it may be possible to model the galactic disk well enough to 
account for its presence, but with a lack of sufficient galactic model, beam model, and the 
analysis tools to include it, we leave this to future work.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{pointing_cartoon.pdf}
\caption{\textcolor{red}{caption!}
\label{fig:pointing}
}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{2d_res.pdf}
\caption[Deep 2D sub-band power spectra]{
Residual two dimensional power spectra for the three sub-bands used to place limits on the 
cosmological signal. The left panels show the low band, centered at 174.7 MHz, or a 
redshift of 7.1. The middle panels show the mid band, centered at 182.4 MHz, or a redshift 
of 6.8. The right panels show the high band, centered at 190.1 MHz, or a redshift of 6.5. 
The red box in the upper left panel shows the window used for averaging to one dimension.
\label{fig:2d_ps_subband}
}
\end{center}
\end{figure*}

@@

Between the coarse band harmonic lines and the reflection line, we do see regions where 
our spectra appear noise-like (positive and negative values). This is encouraging despite 
the leakage at lower $k_{||}$. The red box in the upper left 2D spectrum shows the region of 
$\mathbf{k}$-space we use when averaging to one dimension. We exclude any voxels 
below the solid black horizon line, as well as $k_{||}<0.1$ h Mpc$^{-1}$ due to foreground 
contamination. We limit the $k_{\perp}$ range due to higher power in the coarse bands at 
low $k_{\perp}$, and the poor $uv$ coverage at high $k_{\perp}$, leading to the vertical 
streaks seen on the right side of the 2D spectra. We set our range to be $0.015$ h Mpc
$^{-1} \leq k_{\perp} \leq 0.03$ h Mpc$^{-1}$. This is an aggressive cut, but confidently 
avoids the vertical streaks of leaked power.

One could additionally mask the coarse band harmonic lines when averaging to one 
dimension. However, because $k_{||} \gg k_{\perp}$ within the red box, our spherical shells 
are approximately constant $k_{||}$, so the coarse bands are still isolated in our average. 
We choose to retain them to avoid empty bins, and to help guide the reader when 
comparing the 2D and 1D spectra. While the red box is shown on the 2D plot, the actual 1D 
averaging is done by returning to the full three dimensional power cubes and performing a 
weighted average in shells.

@@

>>>>

\begin{abstract}
The Murchison Widefield Array (MWA) has collected hundreds of hours of Epoch of 
Reionization (EoR) data and now faces the challenge of overcoming foreground and 
systematic contamination to reduce the data to a cosmological measurement. We introduce 
several novel analysis techniques such as cable reflection calibration, high resolution 
gridding kernels, diffuse foreground model subtraction, and quality control methods. Each 
change to the analysis pipeline is tested against a two dimensional power spectrum figure 
of merit to demonstrate improvement. We incorporate the new techniques into a deep 
integration of 32 hours of MWA data. This data set is used to place a systematic-limited 
upper limit on the cosmological power spectrum of $\Delta^2 \leq 2.7 \times 10^4$ mK
$^2$ at $k=0.27$ h~Mpc$^{-1}$ and $z=7.1$, consistent with other published limits, and a 
modest improvement (factor of 1.4) over previous MWA results. While our result is 
systematic limited, we identify several strategies to overcome these systematics in future 
analysis.
\end{abstract}
\keywords{cosmology: observations - cosmology: reionization}
\maketitle

@@

\section{Analysis Pipeline}\label{sec:analysis}
In order to ensure consistency in analysis, the international MWA EoR collaboration has 
defined two independent reference analysis pipelines. The details of this strategy are 
outlined in D.~C.~Jacobs et al. 2016 (in review). This study is based on the FHD-to-
\eppsilon pipe, which is in turn based on the Fast Holographic Deconvolution (FHD
\footnote{\url{https://github.com/EoRImaging/FHD}}, \citealt{Sullivan:2012}) and Error 
Propagated Power Spectrum with Interleaved Observed Noise (\eppsilon
\footnote{\url{https://github.com/EoRImaging/eppsilon}}, B.~J.~Hazelton et al. 2016, in 
prep) packages. The general flow of the pipeline is shown in Figure~\ref{fig:pipe}, and we 
give an overview below.

@@

Under these assumptions we can express the measured, uncalibrated visibility for an 
antenna pair $(i,j)$ as
\begin{equation}
V'_{ij}(\nu) \approx g_i(\nu)g^*_j(\nu)V_{ij}(\nu),
\end{equation}
where $g_i(\nu)$ and $g_j(\nu)$ are the complex gains for antennas $i$ and $j$ 
respectively. Because we are treating polarizations independently, we allow the antenna 
subscript to run over both East-West (E-W) and North-South (N-S) polarizations.

@@

The gridded $uv$ data are then Fourier transformed to create sky-frame images. To avoid 
aliasing we image out 90$^\circ$ from phase center (gridding resolution of a half 
wavelength), and crop the image. We found that cropping the image based on beam value 
resulted in hard edges when integrating images from different snapshots having beams pointed 
in slightly different directions. To avoid the hard edges, we predetermine a set of HEALPix 
pixels to interpolate to, and use the same set for all snapshots on a given field. The final 
cropped field of view for this work is a 21$^\circ$ square centered at RA~$=0$ h, dec~
$=-27^\circ$.

@@

\begin{figure}
\begin{center}
\subfigure{\includegraphics[width=.9\columnwidth]{fourth_line_pre.pdf}}
~
\subfigure{\includegraphics[width=.9\columnwidth]{fourth_line_post.pdf}}
\caption{
\emph{Top:} Single polarization dirty power spectrum formed from the golden data set, 
before implementing cable reflection fitting into the calibration loop. The black arrow points 
to a horizontal band at $k_{||} \approx 0.7$~h~Mpc$^{-1}$, which cannot be accounted for 
by the coarse bands. \emph{Bottom:} After we implement the cable reflection fitting in our 
calibration solutions, we see the reflection line disappears.
\label{fig:cables}
}
\end{center}
\end{figure}

@@

\subsection{Gridding Kernel Resolution}
A similar, low level effect which had the potential to contaminate the EoR window is shown 
in Figure~\ref{fig:beam_res}. The spectra shown are the \emph{model} spectra -- calculated 
by propagating the sky model visibilities through the entire pipeline. Despite our foreground 
model not containing spectral structure, the EoR window in the top panel seems to have a 
floor at a level $\sim 10^7$~mK$^2$~h$^{-3}$~Mpc$^3$, comparable to predicted EoR 
signals. In addition there is a faint line in the upper-left of the plot which has the same slope 
as the wedge, but seems to originate far beyond the horizon.

@@

The source of this floor and super-horizon line was traced to the resolution at which we 
formed the gridding kernel when gridding visibilities. In the interest of computational speed 
and efficiency, the kernel is pre-calculated at a high resolution, then a nearest neighbor 
lookup table is used to approximate the beam values at discrete pixels. The kernel 
resolution used in the top panel of Figure~\ref{fig:beam_res} was 0.04 wavelengths -- much 
smaller than the half wavelength grid corresponding to horizon to horizon imaging. 
However, as a baseline migrates in $\emph{uv}$ coordinates across frequencies, it 
undergoes discrete steps between kernel values used. This effectively results in small 
baseline position errors which shift periodically in frequency, resulting in power being thrown 
up into the window and a relatively strong harmonic at the frequency of the shifting (the faint 
line in the upper left of the window). While we illustrate this effect with a model power 
spectrum, the same problem exists in the data, but is below the noise levels at three hours 
of integration.

@@

It has been shown that subtracting a foreground model strictly within the main lobe of the 
primary beam will not be sufficient to suppress the power spectrum wedge and unlock the 
EoR window \citep{Pober:2016, Thyagarajan:2015, Thyagarajan:2015b}. In principle we 
can repeat the model building described above using additional MWA observations pointed 
away from our field of interest. But until that work is complete we supplement the extent of 
our point source model using additional catalogs. We accomplish this through a hierarchical 
catalog pulling from our early KGS catalog, the MWA Commissioning Survey\footnote{The 
more complete GLEAM Survey \citep[][Hurley-Walker et al., in collaboration review]
{Wayth:2015} was not available at the time of analysis.} \citep[MWACS, ][]
{Hurley-Walker:2014}, the Culgoora catalog \citep{Slee:1977}, and the Molonglo Reference Catalog 
\citep[MRC, ][]{Large:1981}. Source fluxes are prioritized in this order based on our 
confidence in their predicted flux at 182 MHz. We first cluster the source lists to avoid 
redundant sources, using a 3.5 arcmin neighborhood radius, then select the flux from the 
highest priority catalog. Spectral indices were obtained from the MWACS and Culgoora 
catalogs when available, otherwise a two-point spectral index was estimated for Culgoora-
MRC matches or MRC-SUMSS matches. All other sources were given a spectral index of 
$-0.8$. The spectral index was used to extrapolate the flux from the catalog frequency to 
182 MHz, but a uniform spectral index of $-0.8$ is used within our band when forming 
model visibilities for calibration and foreground subtraction.

@@

Because we use the input foreground model to calibrate our visibilities, the gain estimates 
for our two runs differed. In particular we saw the overall flux scale of the calibrated 
visibilities was higher when using the full hierarchical catalog. In order to put both residual 
2D power spectra onto the same scale for comparison, we first divide each pixel by the 
corresponding dirty power spectrum pixel, then subtract to arrive at a ratio difference. 
\begin{equation}\label{eq:diff_ratio}
\mathtt{ratio\;difference = \frac{residual_1}{dirty_1} - \frac{residual_2}{dirty_2}}
\end{equation}
Here we use subscript 1 to represent the MWACS catalog spectra, and 2 for the 
hierarchical catalog spectra. The ratio difference is shown in Figure~\ref{fig:mwacs_ratio}. 
The entire wedge being positive (blue) demonstrates that using the new catalog resulted in 
successfully subtracting higher fractional power. Not only does this indicate we subtract 
more power, but it also confirms that our calibrated data is more closely matched to the 
model, meaning that our calibration solutions in general are more accurate.

@@

We use the jackknife method -- dividing the data into many subgroups -- to filter out bad 
data and detect patterns. A powerful grouping is to divide the data into the observation day 
and ``pointing" (which direction the antennas were pointed while tracking the EoR0 field). 
We show an example of one day's worth of per-pointing power spectra in Figure~
\ref{fig:jackknife}. The pointings are labeled sequentially with $-5$ corresponding to five 
pointing steps prior to zenith transit, $0$ corresponding to zenith, and $+4$ corresponding 
to four steps after zenith. 
This numbering scheme is shown graphically in Figure~\ref{fig:pointing}.
Early in the night ($-5$ through $-3$) the bulk of the galactic plane 
was still above the horizon, and despite being very far from our primary field of view, highly 
contaminated our observations through the sidelobes of the instrument. We then have 
relatively well behaved pointings, with the EoR window dominated by noise, until the final 
pointing of the night when we can see evidence of the galaxy rising again indicated by 
strong lines of power at the edge of the foreground wedge. We saw the same contamination 
on all days of observation and decided to cut all $-5$, $-4$, $-3$, and $+4$ pointings from 
our data set. In principle it may be possible to model the galactic disk well enough to 
account for its presence, but with a lack of sufficient galactic model, beam model, and the 
analysis tools to include it, we leave this to future work.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{pointing_cartoon.pdf}
\caption{This is a cartoon depiction of the numbering scheme used to label pointings in
Figures~\ref{fig:jackknife} and \ref{fig:wedge_cut}. Looking South, a field transits from the
East (left), and the telescope begins observing about 5 pointings before zenith (-5). As the
field drifts overhead, we periodically repoint the telescope to recenter the field. Each shift
increments the pointing label by one, and the zenith pointing is defined as zero.
\label{fig:pointing}
}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{2d_res.pdf}
\caption[Deep 2D sub-band power spectra]{
Residual two dimensional power spectra for the three sub-bands used to place limits on the 
cosmological signal. The left panels show the low band, centered at 174.7 MHz, or a 
redshift of 7.1. The middle panels show the mid band, centered at 182.4 MHz, or a redshift 
of 6.8. The right panels show the high band, centered at 190.1 MHz, or a redshift of 6.5. 
The contours show the window used for averaging to one dimension.
\label{fig:2d_ps_subband}
}
\end{center}
\end{figure*}

@@

Between the coarse band harmonic lines and the reflection line, we do see regions where 
our spectra appear noise-like (positive and negative values). This is encouraging despite 
the leakage at lower $k_{||}$, and motivates us to be selective when binning to one 
dimensional power spectra.

Figure~\ref{fig:slices} shows slices of power that help isolate the contamination. The two 
dimensional power spectrum is the N-S, mid band spectrum from 
Figure~\ref{fig:2d_ps_subband}. We have drawn a horizontal solid blue line to indicate the 
slice used to plot power as a function of $k_{\perp}$ for a fixed $k_{||}$ (top right), and a 
vertical dashed line to show the slice used to plot power as a function of $k_{||}$ for a fixed 
$k_{\perp}$ (bottom right). In the $k_{\perp}$ power plot we can see leakage at low and high
$k_{\perp}$. On the low end this is due to the width of the coarse band harmonics and the
exceptionally bright foregrounds at large scales. On the high end we are seeing the residual
of the vertical streaks due to poor sampling at large $uv$. While the increased noise would
mean that we will down weight the bins at large $k_{\perp}$, the contamination is even
larger, meaning it would bias our estimate even though those bins are down weighted. 
We exclude bins with $u<10\lambda$ and $u>70\lambda$, shown with grey boxes.
Between these two regimes are many bins consistent with the noise level, which we include
in our one dimensional averages.

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{slices.pdf}
\caption{
\emph{Left:} The N-S, $z=6.8$ two dimensional power spectrum repeated from 
Figure~\ref{fig:2d_ps_subband}. Here we have superimposed blue lines to show slices in
$k_{\perp}$ (solid) and $k_{||}$ (dashed). \emph{Top right:} Residual power as a function
of $k_{\perp}$ for fixed $k_{||}$. The grey boxes show regions which will be excluded from
the one dimensional averages. The red dashed line shows the 1-$\sigma$ noise level, and
the vertical black dashed line shows the intersection of this slice with the wedge. 
\emph{Bottom right:} Residual power as a function of $k_{||}$ for fixed $k_{\perp}$. The strong
foreground contamination is evident at low $k_{||}$, and the coarse band harmonic lines
appear as expected. 
\label{fig:slices}
}
\end{center}
\end{figure*}

Similarly we inspect the $k_{||}$ power in the bottom right plot of Figure~\ref{fig:slices}. Here
we see the huge contamination from foregrounds at low $k_{||}$. While the leakage drops 
significantly, our measurements do not reach the noise level until after the first coarse
band harmonic. However, we chose to include bins below the first coarse band with 
$k_{||}>0.15$ h Mpc$^{-1}$ because the cosmological signal is expected to contain 
substantially higher power at large scales, and ultimately these low $k_{||}$ bins provide
our most competitive limits despite being systematic limited. We exclude the coarse band
harmonics by masking out the harmonic bin itself and two bins on either side (total of five
bins per harmonic).

The final mask we apply is the wedge. We found that a small buffer beyond the horizon was
necessary to completely mask out the wedge, consistent with \citealt{Dillon:2015}. We
implement the buffer by extending the horizon line by 15 degrees. This line is shown as the
dashed diagonal line in the left panel of Figure~\ref{fig:slices}.

The various masking described above is summarized with the black contours shown on the
two dimensional power spectra in Figure~\ref{fig:2d_ps_subband}. The contours show
the cuts in two dimensional space, but the masking is actually performed directly in the
three dimensional power spectrum cube and averaged directly to one dimension.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{1D_spectra_comparison.pdf}
\caption{
\textcolor{red}{Caption!}
\label{fig:ps_comparison}
}
\end{figure}
